### 2017-04-27 paper/jfp-submission/evaluation.tex
first draft of error location

% \item \ES{others?}
%
\begin{figure}[htp]
\centerline{
\begin{minipage}{1.2\textwidth}
\includegraphics[width=0.5\linewidth]{trace_size_step.png}
\includegraphics[width=0.5\linewidth]{trace_size_jump.png}
\end{minipage}
}
\vspace{3ex}
\caption{Complexity of the generated traces. 81\% of the combined traces
  have a jump complexity of at most 10, with an average complexity of 7
  and a median of 5.}
\label{fig:results-complexity}
\end{figure}
%
\begin{figure}[htp]
\centerline{
\begin{minipage}{1.2\textwidth}
\includegraphics[width=0.5\linewidth]{user-study-reason.png}
\includegraphics[width=0.5\linewidth]{user-study-fix.png}
\end{minipage}
}
\vspace{3ex}
\caption{A classification of students' explanations and fixes for type
  errors, given either \ocaml's error % message
  or \toolname's
  jump-compressed trace. The students given \toolname's jump-compressed
  trace consistently scored better ($\ge 10\%$) than those given \ocaml's type
  error.}
\label{fig:results-user-study}
\end{figure}

\paragraph{Results}
\label{sec:results-complexity}
The results of the experiment are summarized in
Figure~\ref{fig:results-complexity}.
%
The average number of single-step reductions per trace is 31 for the
\ucsdbench\ dataset (35 for the \uwbench\ dataset) with a maximum of
2,745 (986 for \uwbench) and a median of 17 (also 17 for \uwbench).
%
The average number of jumps per trace is 7 (also 7 for \uwbench) with a
maximium of 353 (185 for \uwbench) and a median of 4 (also 4 for
\uwbench).
%
In both datasets 80\% or more traces have at most 10 jumps.

@@

\subsection{Quantitative Evaluation of Witness Utility}
\label{sec:user-study}
% Finally, to test the explanatory power of our jump-compressed traces, we
% ran a user study (IRB \#2014009900) at the University of Virginia (UVA).
% %
% We included four problems in an exam in the Spring session of UVA's
% undergraduate Programming Languages course (CS 4501).
% %
% We presented the 60 students in the course with ill-typed \ocaml\
% programs and asked them to
% %
% (1) \emph{explain} the type error, and
% %
% (2) \emph{fix} the type error.
% %
% For each problem the student was given the ill-typed program and
% either \ocaml's error message or \toolname's jump-compressed trace.
%
We assigned four problems to the ($n=60$) students in the course: the
@sumList@, @digitsOfInt@, and @wwhile@ programs from
\S~\ref{sec:advantage-traces}, as well as the following @append@ program
%
\begin{ecode}
  let append x l =
    match x with
    | []   -> l
    | h::t -> h :: t :: l
\end{ecode}
%
which triggers an occurs-check error on line 4.
%
For each problem the students were given the ill-typed program and
either \ocaml's error message or \toolname's jump-compressed trace.
%
Due to the nature of an in-class exam, not every student answered every
question; we received between 13 and 28 (out of a possible 30) responses
for each problem-tool pair.

@@

@@

>>>>

% \item \ES{others?}
%
\begin{figure}[t]
\centerline{
\begin{minipage}{1.2\textwidth}
\includegraphics[width=0.5\linewidth]{trace_size_step.png}
\includegraphics[width=0.5\linewidth]{trace_size_jump.png}
\end{minipage}
}
\vspace{3ex}
\caption{Complexity of the generated traces. 81\% of the combined traces
  have a jump complexity of at most 10, with an average complexity of 7
  and a median of 5.}
\label{fig:results-complexity}
\end{figure}
%
\paragraph{Results}
\label{sec:results-complexity}
The results of the experiment are summarized in
Figure~\ref{fig:results-complexity}.
%
The average number of single-step reductions per trace is 31 for the
\ucsdbench\ dataset (35 for the \uwbench\ dataset) with a maximum of
2,745 (986 for \uwbench) and a median of 17 (also 17 for \uwbench).
%
The average number of jumps per trace is 7 (also 7 for \uwbench) with a
maximium of 353 (185 for \uwbench) and a median of 4 (also 4 for
\uwbench).
%
In both datasets 80\% or more traces have at most 10 jumps.

@@

\subsection{Quantitative Evaluation of Witness Utility}
\label{sec:user-study}
% Finally, to test the explanatory power of our jump-compressed traces, we
% ran a user study (IRB \#2014009900) at the University of Virginia (UVA).
% %
% We included four problems in an exam in the Spring session of UVA's
% undergraduate Programming Languages course (CS 4501).
% %
% We presented the 60 students in the course with ill-typed \ocaml\
% programs and asked them to
% %
% (1) \emph{explain} the type error, and
% %
% (2) \emph{fix} the type error.
% %
% For each problem the student was given the ill-typed program and
% either \ocaml's error message or \toolname's jump-compressed trace.
%
We assigned four problems to the 60 students in the course: the
@sumList@, \hbox{@digitsOfInt@,} and @wwhile@ programs from
\S~\ref{sec:advantage-traces}, as well as the following @append@ program
%
\begin{ecode}
  let append x l =
    match x with
    | []   -> l
    | h::t -> h :: t :: l
\end{ecode}
%
which triggers an occurs-check error on line 4.
%
For each problem the students were given the ill-typed program and
either \ocaml's error or \toolname's jump-compressed trace.
%
Due to the nature of an in-class exam, not every student answered every
question; we received between 13 and 28 (out of a possible 30) responses
for each problem-tool pair.

@@

\begin{figure}[t]
\centerline{
\begin{minipage}{1.2\textwidth}
\includegraphics[width=0.5\linewidth]{user-study-reason.png}
\includegraphics[width=0.5\linewidth]{user-study-fix.png}
\end{minipage}
}
\vspace{3ex}
\caption{A classification of students' explanations and fixes for type
  errors, given either \ocaml's error % message
  or \toolname's
  jump-compressed trace. The students given \toolname's jump-compressed
  trace consistently scored better ($\ge 10\%$) than those given \ocaml's type
  error.}
\label{fig:results-user-study}
\end{figure}

@@

\input{locating}
